Compare CMC and HBCC differential expression

### 2017-08-30 code/Rmd/CMC_HBCC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Added markdown to process CMC and HBCC samples together

knit2synapse::knitToFolderEntity(file = "./CMC_HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'CMC and HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN')
```

@@

thisFileName <- 'CMC_HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd'

@@

COVARIATES = rbindlist(list(CMC = COVARIATES_CMC, 
                            HBCC = COVARIATES_HBCC), 
                       use.names = T, fill = T, idcol = 'Study')
```

### Data preprocessing
Filter DLPFC SCZ and Control samples alone
```{r preprocess.data, fig.height=10, fig.width=15}
# Filter all ACC samples and Other samples
COVARIATES = COVARIATES %>%
  dplyr::filter(Dx.Tissue %in% c("SCZ_DLPFC", "Control_DLPFC"))

COVARIATES %>%
  dplyr::group_by(Dx.Tissue, Study) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::spread(Study, count) %>% 
  kable()

@@

Age match CMC and HBCC (per Dx.Tissue category)
```{r preprocess.data1}
# Filter all ACC samples and Other samples
max.age = COVARIATES %>%
  dplyr::group_by(Dx.Tissue, Study) %>%
  dplyr::filter(Study == 'CMC') %>%
  dplyr::summarise(mn = quantile(Age_of_Death, 0.5))

COVARIATES = COVARIATES %>%
  dplyr::filter((Dx.Tissue == max.age$Dx.Tissue[1] & Age_of_Death <= max.age$mn[1]) |
                  (Dx.Tissue == max.age$Dx.Tissue[2] & Age_of_Death <= max.age$mn[2]))

COVARIATES %>%
  dplyr::group_by(Dx.Tissue, Study) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::spread(Study, count) %>% 
  kable()
```

PMI match CMC and HBCC (per Dx.Tissue category)
```{r preprocess.data2}
max.pmi = COVARIATES %>%
  dplyr::group_by(Dx.Tissue) %>%
  dplyr::filter(Study == 'HBCC') %>%
  dplyr::summarise(mn = quantile(PMI, 0.5))

COVARIATES = COVARIATES %>%
  dplyr::filter((Dx.Tissue == max.age$Dx.Tissue[1] & PMI <= max.pmi$mn[1]) |
                  (Dx.Tissue == max.age$Dx.Tissue[2] & PMI <= max.pmi$mn[2]))

COVARIATES %>%
  dplyr::group_by(Dx.Tissue, Study) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::spread(Study, count) %>% 
  kable()
```

@@

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c('Study', 'Individual_ID', 'Institution', 'Gender', 'LibraryBatch', 'Dx.Tissue', 'RibozeroBatch',
                      'FlowcellBatch')
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate")

@@

### Explore metatdata
```{r data.explore, fig.width = 15, fig.height = 10}
my.theme <- theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1), plot.title=element_text(hjust=0.5))

p1 = ggpubr::ggarrange(plotlist = p, ncol = 4, nrow = 2)
p1
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Also remove genes with missing gene length and percentage GC content
```{r cpmnormalisation}
COUNT[is.na(COUNT)] = 0
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Dx.Tissue), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>%
  dplyr::mutate(label = SampleID)
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Institution, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= label), size=4, hjust=0)
p

tmp = tidyr::separate(COVARIATES, Dx.Tissue, c('Dx', 'Tissue'), sep = '_') %>%
  group_by(Study, Dx, Tissue) %>%
  summarise(count = n()) %>%
  spread(Dx, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples from `r length(unique(COVARIATES$Individual_ID))` unique individuals

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_')

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Institution, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p
```
Tree based clustering of samples
```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c("Institution", "Gender", "LibraryBatch", "Dx.Tissue")])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

@@

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE}
# Plot abberent distribution of logcpm counts
tmp1 = (CQN.GENE_EXPRESSION$E) %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  tidyr::gather(SampleID, logCPM, -ensembl_gene_id) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID') %>%
              tidyr::separate(Dx.Tissue, c('Dx', 'Tissue'), sep = '_'))

p = ggplot(tmp1, aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme(legend.position = 'NONE') + facet_grid(Dx+.~Tissue, scale = 'free')
p
```

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>%
  dplyr::mutate(label = SampleID)
# plotdata$label[!(plotdata$SampleID %in% top.nsamples)] = ''

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Institution, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
```

```{r decompse.normalise.data2.1, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c('Dx.Tissue','Institution')])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

@@

WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp[,c('Dx.Tissue','Institution')]))
```

@@

### Differential expression analysis (SCZ - Control)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=15, fig.width=20}
# Fit contrast
contrast = makeContrasts(contrasts=c("Dx.Tissue.StudySCZ_DLPFC_CMC-Dx.Tissue.StudyControl_DLPFC_CMC",
                                     "Dx.Tissue.StudySCZ_DLPFC_HBCC-Dx.Tissue.StudyControl_DLPFC_HBCC"),
                         levels = colnames(ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

@@

### Differential expression analysis (SCZ - Control gender specific)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp1, fig.height=15, fig.width=20}
COVARIATES$Dx.Tissue.Study.Gender = paste(COVARIATES$Dx.Tissue.Study,
                                          COVARIATES$Gender,
                                          sep = '_') %>%
  factor()

@@

# Fit contrast
contrast = makeContrasts(contrasts=
                           c("Dx.Tissue.Study.GenderSCZ_DLPFC_CMC_Female-Dx.Tissue.Study.GenderControl_DLPFC_CMC_Female",
                             "Dx.Tissue.Study.GenderSCZ_DLPFC_CMC_Male-Dx.Tissue.Study.GenderControl_DLPFC_CMC_Male",
                             "Dx.Tissue.Study.GenderSCZ_DLPFC_HBCC_Female-Dx.Tissue.Study.GenderControl_DLPFC_HBCC_Female",
                             "Dx.Tissue.Study.GenderSCZ_DLPFC_HBCC_Male-Dx.Tissue.Study.GenderControl_DLPFC_HBCC_Male"),
                         levels = colnames(ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

@@

# Code
CODE <- Folder(name = "CMC and HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

@@

# Store differential expression results
all.diff.exp %>%
  rbindlist(use.names = T, fill = T) %>%
  write.table(file = 'CMC_HBCC_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('CMC_HBCC_DLPFC_DiffExpression.tsv', 
name = 'Differential Expression Results (Dx.Tissue)', 
parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |

>>>>

knit2synapse::knitToFolderEntity(file = "./CMC_HBCC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'CMC and HBCC - ACC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN')
```

@@

thisFileName <- 'CMC_HBCC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd'

@@

COVARIATES = rbindlist(list(CMC = COVARIATES_CMC, 
                            HBCC = COVARIATES_HBCC), 
                       use.names = T, fill = T, idcol = 'Study')
COVARIATES$Dx.Tissue.Study = paste(COVARIATES$Dx.Tissue, COVARIATES$Study, sep = '_')
```

### Data preprocessing
```{r preprocess.data, fig.height=10, fig.width=15}
COVARIATES = COVARIATES %>%
  dplyr::filter(!(Dx.Tissue %in% c('BP_DLPFC', 'Other_ACC', 'Other_DLPFC')))

COVARIATES %>%
  dplyr::group_by(Dx.Tissue.Study) %>%
  dplyr::summarise(count = n()) %>% 
  kable()

@@

@@

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c('Individual_ID', 'Institution', 'Gender', 'LibraryBatch', 'Dx.Tissue.Study',
                      'RibozeroBatch', 'FlowcellBatch')
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate",
                    "IntergenicRate", "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate")

@@

### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Also remove genes with missing gene length and percentage GC content
```{r cpmnormalisation}
COUNT[is.na(COUNT)] = 0
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Dx.Tissue.Study), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue.Study, c('Dx','Tissue', 'Study'), sep = '_') %>%
  dplyr::mutate(label = SampleID)
# plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Study, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= label), size=4, hjust=0)
p

tmp = tidyr::separate(COVARIATES, Dx.Tissue.Study, c('Dx', 'Tissue', 'Study'), sep = '_') %>%
  group_by(Study, Dx, Tissue, Study) %>%
  summarise(count = n()) %>%
  spread(Dx, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples from `r length(unique(COVARIATES$Individual_ID))` unique individuals

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue.Study, c('Dx','Tissue','Study'), sep = '_')

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Study, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p
```
Tree based clustering of samples
```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c("Institution", "Gender", "LibraryBatch", "Dx.Tissue.Study")])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

@@

@@

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue.Study, c('Dx','Tissue','Study'), sep = '_') %>%
  dplyr::mutate(label = SampleID)
# plotdata$label[!(plotdata$SampleID %in% top.nsamples)] = ''

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Study, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
```

```{r decompse.normalise.data2.1, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c('Dx.Tissue.Study','Institution')])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0

@@

WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp[,c('Dx.Tissue.Study','Institution')]))
```

@@

### Differential expression analysis (SCZ - Control)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=15, fig.width=20}
# Fit contrast
contrast = makeContrasts(contrasts=c("Dx.Tissue.StudySCZ_DLPFC_CMC_-Dx.Tissue.StudyControl_DLPFC_CMC_",
                                     "Dx.Tissue.StudySCZ_DLPFC_HBCC_-Dx.Tissue.StudyControl_DLPFC_HBCC_",
                                     "Dx.Tissue.StudySCZ_ACC_CMC_-Dx.Tissue.StudyControl_ACC_CMC_"),
                         levels = colnames(ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

@@

### Differential expression analysis (SCZ - Control gender specific)
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp1, fig.height=15, fig.width=20}
COVARIATES$Dx.Tissue.Study.Gender = paste0(COVARIATES$Dx.Tissue.Study,
                                           COVARIATES$Gender) %>%
  factor()

@@

# Fit contrast
contrast = makeContrasts(contrasts=
                           c("Dx.Tissue.Study.GenderSCZ_DLPFC_CMC_Female-Dx.Tissue.Study.GenderControl_DLPFC_CMC_Female",
                             "Dx.Tissue.Study.GenderSCZ_DLPFC_CMC_Male-Dx.Tissue.Study.GenderControl_DLPFC_CMC_Male",
                             "Dx.Tissue.Study.GenderSCZ_DLPFC_HBCC_Female-Dx.Tissue.Study.GenderControl_DLPFC_HBCC_Female",
                             "Dx.Tissue.Study.GenderSCZ_DLPFC_HBCC_Male-Dx.Tissue.Study.GenderControl_DLPFC_HBCC_Male",
                             "Dx.Tissue.Study.GenderSCZ_ACC_CMC_Female-Dx.Tissue.Study.GenderControl_ACC_CMC_Female",
                             "Dx.Tissue.Study.GenderSCZ_ACC_CMC_Male-Dx.Tissue.Study.GenderControl_ACC_CMC_Male"),
                         levels = colnames(ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

@@

# Code
CODE <- Folder(name = "CMC and HBCC - ACC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

@@

# Store differential expression results
all.diff.exp %>%
  rbindlist(use.names = T, fill = T) %>%
  write.table(file = 'CMC_HBCC_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('CMC_HBCC_DLPFC_DiffExpression.tsv', 
name = 'Differential Expression Results (Dx.Tissue)', 
parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |

### 2017-08-30 code/Rmd/CMC_HBCC_COMPARISON.Rmd
Added markdown to process CMC and HBCC samples together

### Data download
```{r download.data, cache=TRUE}
# Get differential expression results
diff.exp.ids = c(CMC = 'syn9874406',
                 CMC_qSVA = 'syn10341319',
                 HBCC = 'syn10263511',
                 HBCC_qSVA = 'syn10294725')

@@

### Analyse results
Replication rate based on number of gene differentiallty expressed in the same directiona at an FDR of 0.05
```{r anlz.results}
rep.rate = list()
for (pval in seq(0,-6,-1)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    dplyr::mutate(Direction = factor(sign(logFC), levels = c('-1','1'), labels = c('-1' = 'DOWN','1' = 'UP'))) %>%
    plyr::dlply(.(Model, Direction), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

@@

  rep.rate = c(rep.rate, list(data.frame(fdr = 10^pval, wo.qsva = wo.qsva, w.qsva = w.qsva,
                                         n.wo.qsva = n.wo.qsva, n.w.qsva = n.w.qsva)))
}
rep.rate = rbindlist(rep.rate)
rep.rate %>%
  dplyr::select(fdr, wo.qsva, w.qsva) %>%
  tidyr::gather(method, rep.rate, -fdr) %>%
  dplyr::mutate(rep.rate = rep.rate * 100) %>%
  dplyr::left_join(rep.rate %>%
                     dplyr::select(fdr, n.wo.qsva, n.w.qsva) %>%
                     tidyr::gather(method, ncount, -fdr) %>%
                     dplyr::mutate(method = gsub('n.','',method))) %>%
  dplyr::filter(fdr <= 1e-1) %>%
  ggplot(aes(x=fdr, y=rep.rate, color = method)) + geom_point(aes(size = ncount)) + geom_line() + scale_x_log10() + xlab('FDR') + ylab('Replication Rate (%)')
```
Replication rate based on qvalue
```{r anlz.results1}
rep.rate = list()
for (pval in c(-1, -1.30103, -2)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    plyr::dlply(.(Model), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'CMC', ensembl_gene_id %in% de.genes$HBCC) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = data.frame(method = 'wo.qsva', ref.data = 'HBCC', rep.data = 'CMC',
                  rep.rate = sum(tmp$significant)/length(tmp$significant), 
                  ncount = sum(tmp$significant))

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'HBCC', ensembl_gene_id %in% de.genes$CMC) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = rbind(rs,
             data.frame(method = 'wo.qsva', ref.data = 'CMC', rep.data = 'HBCC',
                        rep.rate = sum(tmp$significant)/length(tmp$significant), 
                        ncount = sum(tmp$significant)))

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'CMC_qSVA', ensembl_gene_id %in% de.genes$HBCC_qSVA) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = rbind(rs,
             data.frame(method = 'w.qsva', ref.data = 'HBCC', rep.data = 'CMC',
                        rep.rate = sum(tmp$significant)/length(tmp$significant), 
                        ncount = sum(tmp$significant)))

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'HBCC_qSVA', ensembl_gene_id %in% de.genes$CMC_qSVA) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = rbind(rs,
             data.frame(method = 'w.qsva', ref.data = 'CMC', rep.data = 'HBCC',
                        rep.rate = sum(tmp$significant)/length(tmp$significant), 
                        ncount = sum(tmp$significant)))

>>>>

### Data download
```{r download.data, cache=TRUE}
# Get differential expression results
diff.exp.ids = c(CMC = 'syn9874406',
                 CMC_qSVA = 'syn10341319',
                 HBCC = 'syn10263511',
                 HBCC_qSVA = 'syn10294725',
                 MATCHED = 'syn10490519')

@@

### Analyse results
Replication rate based on number of gene differentiallty expressed in the same directiona at an FDR of 0.05
```{r anlz.results}
rep.rate = list()
for (pval in seq(0,-4,-1)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    dplyr::mutate(Direction = factor(sign(logFC), levels = c('-1','1'), labels = c('-1' = 'DOWN','1' = 'UP'))) %>%
    plyr::dlply(.(Model, Direction), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

@@

  de.genes = diff.exp %>%
    dplyr::filter(Comparison %in% c('SCZ_DLPFC_CMC-Control_DLPFC_CMC', 'SCZ_DLPFC_HBCC-Control_DLPFC_HBCC')) %>%
    dplyr::mutate(Direction = factor(sign(logFC), levels = c('-1','1'), labels = c('-1' = 'DOWN','1' = 'UP'))) %>%
    plyr::dlply(.(Comparison, Model, Direction), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

  l1 = length(intersect(de.genes$`SCZ_DLPFC_CMC-Control_DLPFC_CMC.MATCHED.DOWN`,
                        de.genes$`SCZ_DLPFC_HBCC-Control_DLPFC_HBCC.MATCHED.DOWN`))
  l2 = length(intersect(de.genes$`SCZ_DLPFC_CMC-Control_DLPFC_CMC.MATCHED.UP`, 
                        de.genes$`SCZ_DLPFC_HBCC-Control_DLPFC_HBCC.MATCHED.UP`))
  l3 = length(unique(Reduce(c, de.genes)))
  matched = (l1+l2)/l3
  n.matched = l1+l2

  rep.rate = c(rep.rate, list(data.frame(fdr = 10^pval, 
                                         wo.qsva = wo.qsva, w.qsva = w.qsva, matched = matched,
                                         n.wo.qsva = n.wo.qsva, n.w.qsva = n.w.qsva, n.matched = n.matched)))
}
rep.rate = rbindlist(rep.rate)
rep.rate %>%
  dplyr::select(fdr, wo.qsva, w.qsva, matched) %>%
  tidyr::gather(method, rep.rate, -fdr) %>%
  dplyr::mutate(rep.rate = rep.rate * 100) %>%
  dplyr::left_join(rep.rate %>%
                     dplyr::select(fdr, n.wo.qsva, n.w.qsva, n.matched) %>%
                     tidyr::gather(method, nOverlap, -fdr) %>%
                     dplyr::mutate(method = gsub('n.','',method))) %>%
  dplyr::filter(fdr <= 1e-1) %>%
  ggplot(aes(x=fdr, y=rep.rate, color = method)) + geom_point(aes(size = nOverlap)) + geom_line() + scale_x_log10() + xlab('FDR') + ylab('Replication Rate (%)') + ggtitle('CMC - HBCC - DLPFC')
```
Replication rate based on qvalue
```{r anlz.results1}
rep.rate = list()
for (pval in c(-1, -1.30103, -2)){
  de.genes = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC') %>%
    plyr::dlply(.(Model), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'CMC', ensembl_gene_id %in% de.genes$HBCC) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = data.frame(method = 'wo.qsva', ref.data = 'HBCC', rep.data = 'CMC',
                  rep.rate = 1-tmp$pi0, 
                  ncount = sum(tmp$significant))

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'HBCC', ensembl_gene_id %in% de.genes$CMC) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = rbind(rs,
             data.frame(method = 'wo.qsva', ref.data = 'CMC', rep.data = 'HBCC',
                        rep.rate = 1-tmp$pi0, 
                        ncount = sum(tmp$significant)))

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'CMC_qSVA', ensembl_gene_id %in% de.genes$HBCC_qSVA) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = rbind(rs,
             data.frame(method = 'w.qsva', ref.data = 'HBCC', rep.data = 'CMC',
                        rep.rate = 1-tmp$pi0, 
                        ncount = sum(tmp$significant)))

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC-Control_DLPFC', Model == 'HBCC_qSVA', ensembl_gene_id %in% de.genes$CMC_qSVA) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = rbind(rs,
             data.frame(method = 'w.qsva', ref.data = 'CMC', rep.data = 'HBCC',
                        rep.rate = 1-tmp$pi0, 
                        ncount = sum(tmp$significant)))

  de.genes = diff.exp %>%
    dplyr::filter(Comparison %in% c('SCZ_DLPFC_CMC-Control_DLPFC_CMC', 'SCZ_DLPFC_HBCC-Control_DLPFC_HBCC')) %>%
    plyr::dlply(.(Comparison), .fun = function(x){
      x$ensembl_gene_id[x$adj.P.Val <= 10^pval] %>% unique()
    })

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC_CMC-Control_DLPFC_CMC', 
                  ensembl_gene_id %in% de.genes$`SCZ_DLPFC_HBCC-Control_DLPFC_HBCC`) %>%
    dplyr::select(P.Value)

  if (dim(tmp)[1] != 0){
    tmp %>%
      qvalue::qvalue(fdr.level = 10^pval)
    rs = rbind(rs,
               data.frame(method = 'matched', ref.data = 'HBCC', rep.data = 'CMC',
                          rep.rate = 1-tmp$pi0, 
                          ncount = sum(tmp$significant)))
  } else {
    rs = rbind(rs,
               data.frame(method = 'matched', ref.data = 'HBCC', rep.data = 'CMC',
                          rep.rate = 0, 
                          ncount = 0))
  }

  tmp = diff.exp %>%
    dplyr::filter(Comparison == 'SCZ_DLPFC_HBCC-Control_DLPFC_HBCC', 
                  ensembl_gene_id %in% de.genes$`SCZ_DLPFC_CMC-Control_DLPFC_CMC`) %>%
    dplyr::select(P.Value) %>%
    qvalue::qvalue(fdr.level = 10^pval)
  rs = rbind(rs,
             data.frame(method = 'matched', ref.data = 'CMC', rep.data = 'HBCC',
                        rep.rate = 1-tmp$pi0, 
                        ncount = sum(tmp$significant)))
